### 2021-04-26 assertions/doc/thesis-bernhardt/chapters/5-offline_design_tezos.tex
Finish revision chpt 5

\subsection{Proof-of-stake in Tezos}
In Tezos, contracts which have staked a minimum amount of tokens, called a roll, can participate in the consensus mechanism. When participating, a contract has a chance to obtain the role of either a baker or an endorser. Contracts who don't own enough tokens, or infrastructure, to participate directly, can delegate their baking and endorsing rights to other contracts. The rights to bake or endorse are determined and assigned at the beginning of each cycle, which consists of a specified number of blocks. For baking, a random roll is selected for each block level and the rights are assigned to its owner. The block produced by that baker is signed by a fixed number of endorsers (32 as of protocol 007 Delphi), which also have been assigned endorsing rights for this block level by a random selection of rolls. Since participants can stake more than one roll, they may be assigned several endorsement slots at the same block level.

@@

\subsection{Gas model}
Tezos stores and transmits data as byte sequences --- in order to obtain a typed representation of their value for interpretation, a byte sequence is first deserialised into Micheline and subsequently parsed into a typed AST. Conversely, before transmitting or storing something on the blockchain, the typed representation is first unparsed into Micheline and then serialised. Since these working steps also entail computational effort, they consume gas and thus account for some of the transaction fees. The gas consumption of an operation (e.g., a transaction or a contract origination) is thus composed of the following positions \cite{morley_gasmodel}\cite{tezos_repo} on top of a base gas fee:
\begin{enumerate}
\item \textbf{Reading costs} --- apply for reading the contract code and storage from the blockchain and, on top of a base cost, depend on the amount of bytes read
\item \textbf{Deserialization costs} --- depend on the Micheline expression and the size of the byte sequence
\item \textbf{Parsing costs} --- are composed of three types of costs:
	\begin{itemize}
	\item type parsing --- apply when a Micheline node is converted into a valid type
	\item data parsing --- apply when a node is converted into the value of a known type and depends on the size of the value
	\item code parsing --- apply when the instructions of a program are type checked and depends on the number and types of instructions. Some instructions are expensive, such as \texttt{IF} (both branches need to be checked and compared) or \texttt{CREATE\_CONTRACT} (requires type check of invoked contract)
	\end{itemize}
\item \textbf{Type comparison costs} --- apply when types are checked for equality (e.g. when type checking the branches of the \texttt{IF} instruction) or during contract interpretation
\item \textbf{Interpretation costs} --- apply for each interpreted instruction and depend on their complexity.
\item \textbf{Unparsing costs} --- apply when converting typed data to untyped Micheline nodes and depend on the data type and size
\item \textbf{Serialization costs} --- apply when serializing Micheline nodes to byte sequences and depend on the expression and its size
\item \textbf{Writing costs} --- apply when writing to the internal database and depend on the amount of bytes. A base fee applies for each additional byte of storage.
\end{enumerate}
If a transaction emits internal operations, their gas consumption is computed in the same way and are added to the total gas consumption of the external operation.

@@

\subsection{Monolithic orchestration}
In the monolithic approach, the assertion and parent code are merged into a single Smart Contract. This tightly couples and unites the code in one self-contained unit. As shown in \figref{fig:mono_eps}, the assertions are appended to the original contract as separate entrypoints. Since the \texttt{random} instruction is only available in the execution mode for assertion checking, the assertion code cannot be directly prepended to the respective production code. Otherwise, transactions invoking such an entrypoint could not be included into blocks, as these are validated in the normal execution mode.
\begin{figure}[h]
\centering
  \includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_ep_basic.jpg}
	\caption{Monolithic assembly - appending assertions as separate entrypoints}
	\label{fig:mono_eps}
\end{figure}

@@

If the pattern excludes any special values of the data type (e.g., \texttt{cons head tail} excludes empty lists), the generated code should reflect this. Excluded values should never cause the assertion to fail. In the example of \texttt{cons}, the generated code should thus contain the branching shown in \lstref{lst:cons}. The branch in line 1 is executed if the list contains at least one element, and should contain the assertion code. If the list is empty, the branch in line 2 should simply return successfully. 
\begin{lstlisting}[language=Michelson, label=lst:cons, caption=Exclusion of empty lists in the assertion]
IF_CONS ( <assertion body> )
        ( <return ([], ())>)
\end{lstlisting}
% Translation from quantifiers to random generators!

@@

\section{Cost analysis}\label{sec:cost_analysis_distributed}\todo{rename to evaluation and add some more stuff}
What remains to be evaluated is the cost of checking a formula with the proposed approach, and how they relate to the costs for a local validation which were analysed in \secref{sec:usecase_cost}. The previous analysis defined \eqref{eq:gas_transaction} to calculate the gas consumption of a transaction, including the emitted operations. For each validator, the transaction calling the manager contract emits $t+1$ internal operations, whose gas consumptions are also dependent of the input parameter. Based on the $t+1$ additional base, as well as deserialization and parsing costs of the parameter alone, it can be concluded that the total gas consumption of $n$ total distributed test runs is higher than the cost of checking $n$ values locally. \\
The differential can be measured by implementing the orchestration scheme for the two dummy contracts given in \secref{sec:usecase_cost}. Appendix \ref{apx} contains the code of all three components for each of them. In order to measure the gas consumption for a comparable amount of executions as during the initial cost analysis, the probability threshold $c$ is set to $\frac{1}{e}$, s.t. that the necessary number of total test runs is $n$. However, it needs to be pointed out, that the actual number of test runs executed can only be a multiple of the number of validators (cf. \eqref{eq:t_validator}). \figref{fig:cost_distributed} shows the reported gas consumption per validator, i.e., a $32^{th}$ of the total cost for checking an assertion for the given threshold. Due to \eqref{eq:t_validator}, the cost function approximates a step function.
\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{figures/5-offline_tezos/cost_analysis}
\caption{Gas consumption per validator of transactions calling \texttt{Foo} and \texttt{Bar} for increasing input sizes}
\label{fig:cost_distributed}
\end{figure}
The results show that the cost incurred by a single validator checking $t$ values is already considerably higher than by checking the property locally. Moreover, the cost-performance ratio is even worse, as the confidence that the property is indeed satisfied is only around 63\% with the given parameters. In conclusion to these results, it may be worth looking into some alternative approaches. \secref{sec:alt_random} already mentions the possibility to coordinate the validators for a systematic iteration of the search space. Alternatively, the proposed orchestration could be modified, s.t. the manager and assertion code are not implemented as separate contracts, but with one single contract. Instead of $(t+1)$ internal operations, one only has to pay for one internal operation that calls the parent contract, hence avoiding the base, deserialization and parsing costs for each test run. Similar to the monolithic orchestration approach, this increases the complexity of the compilation process.\\ Another idea worth exploring is the adaption of the blockchain protocol to avoid user costs for assertion checking, similar to the regular validation of blocks \cite{tezos_docs}. Instead of being paid by the user in gas, validators could be given a reward for checking an assertion, or a particularly high one for finding a counterexample.

\todo{Cheaper for the network if not all validators have to execute the whole local check! however, placing these costs on the users will cause them to use the local approach -> users need incentives to use it too! -> blockchain protocol could/should solve this! (e.g. use rewards instead of costs)}
\todo{Every transaction is processed at every node in the network,which limits throughput}

\section{Representing counterexamples}\label{sec:counterexample}
\todo{Adapt -> counterexample as separate contract? failwith returns address and data and validator broadcasts normal tx to this contract? is included in block and validated as any other normal tx. how to reject C(x) if A(C, x,y) is on the chain?}

There still remains an open question concerning the proposed implementation that could be answered in detail within the scope of this thesis - the representation and validation of a counterexamples. The interaction scheme in \figref{fig:interaction_modular} suggests, that validators publish an instance of a counterexample to the network if they found one. However, it has yet to be specified how the counterexample is represented and double-checked by the other validators. With the \texttt{failwith} instruction, the top element of the stack can be exposed \cite{tezos_docs}, providing a way to return an interpretable expression from the interpretation context \cite{tezos_repo}. Thus, as a first approximation, the counterexample could be represented as a tuple of assertion code and a list of randomly generated values. For instance, the counterexample for the assumption ``p is a prime'' (cf. \eqref{eq:prime}) is represented by \\
\texttt{(n >= 2 \&\& n <= sqrt(p) \&\& p\%n = 0, <random value for n>)}. \\
For validation of the counterexample, this tuple, together with the respective operation hash of the initial transaction this counterexample refers to, is published to the network. The other validators then interpret the given code with the respective value(s) and either confirm or object the counterexample. As Tezos transmits data as byte sequences, the counterexample needs to be unparsed and serialized, or deserialized and parsed respectively. If the cost for checking assertions is paid for be the user (in form of gas), then these costs have to be added to the total costs as well.\\
In order to prevent denial-of-service attacks by spamming the network with false counterexamples, the protocol should implement penalties for such cases. Details about this and possible rewards for valid counterexamples should be considered in the protocol design.

\todo{Make clear that we only engage validators on Tezos (not all nodes)}
\todo{What happens if a validator has multiple endorsing rights? -> open issues section?}

>>>>

\subsection{Proof-of-stake in Tezos}
In Tezos, contracts which have staked a minimum amount of tokens, called a roll, can participate in the consensus mechanism. When participating, a contract has a chance to obtain the role of either a baker or an endorser. Contracts who don't own enough tokens, or infrastructure, to participate directly, can delegate their baking and endorsing rights to other contracts. The rights to bake or endorse are determined and assigned at the beginning of each cycle, which consists of a specified number of blocks. For baking, a random roll is selected for each block level and the rights are assigned to its owner. The block produced by that baker is signed by a fixed number of endorsers\footnote{For consistency, endorsers are referred to as ``validators'' in this chapter} (32 as of protocol 007 Delphi), which also have been assigned endorsing rights for this block level by a random selection of rolls. Since participants can stake more than one roll, they may be assigned several endorsement slots at the same block level.

@@

\subsection{Gas model}
Tezos stores and transmits data as byte sequences --- in order to obtain a typed representation of their value for interpretation, a byte sequence is first deserialised into Micheline and subsequently parsed into a typed AST. Conversely, before transmitting or storing something on the blockchain, the typed representation is first unparsed into Micheline and then serialised. Since these working steps also entail computational effort, they consume gas and thus account for some of the transaction fees. The gas consumption of an operation (e.g., a transaction or a contract origination) is thus composed of the following positions \cite{morley_gasmodel}\cite{tezos_repo} on top of a base gas fee:
\begin{enumerate}
\item \textbf{Reading costs} --- apply for reading the contract code and storage from the blockchain and, on top of a base cost, depend on the amount of bytes read
\item \textbf{Deserialization costs} --- depend on the Micheline expression and the size of the byte sequence. Apply lazily, thus the deserialization of each value only has to be paid once
\item \textbf{Parsing costs} --- are composed of three types of costs:
	\begin{itemize}
	\item type parsing --- apply when a Micheline node is converted into a valid type
	\item data parsing --- apply when a node is converted into the value of a known type and depends on the size of the value
	\item code parsing --- apply when the instructions of a program are type checked and depends on the number and types of instructions. Some instructions are expensive, such as \texttt{IF} (both branches need to be checked and compared) or \texttt{CREATE\_CONTRACT} (requires type check of invoked contract)
	\end{itemize}
\item \textbf{Type comparison costs} --- apply when types are checked for equality (e.g. when type checking the branches of the \texttt{IF} instruction) or during contract interpretation
\item \textbf{Interpretation costs} --- apply for each interpreted instruction and depend on their complexity.
\item \textbf{Unparsing costs} --- apply when converting typed data to untyped Micheline nodes and depend on the data type and size
\item \textbf{Serialization costs} --- apply when serializing Micheline nodes to byte sequences and depend on the expression and its size
\item \textbf{Writing costs} --- apply when writing to the internal database and depend on the amount of bytes. A base gas fee is burned (destroyed) for each additional byte of storage.
\end{enumerate}
If a transaction emits internal operations, their gas consumption is computed in the same way and are added to the total gas consumption of the external operation.

@@

\subsection{Monolithic orchestration}\label{sec:monolithic}
In the monolithic approach, the assertion and parent code are merged into a single Smart Contract. This tightly couples and unites the code in one self-contained unit. As shown in \figref{fig:mono_eps}, the assertions are appended to the original contract as separate entrypoints. Since the \texttt{random} instruction is only available in the execution mode for assertion checking, the assertion code cannot be directly prepended to the respective production code. Otherwise, transactions invoking such an entrypoint could not be included into blocks, as these are validated in the normal execution mode.
\begin{figure}[h]
\centering
  \includegraphics[width=0.5\textwidth]{figures/5-offline_tezos/pipeline_output_mono_ep_basic.jpg}
	\caption{Monolithic assembly - appending assertions as separate entrypoints}
	\label{fig:mono_eps}
\end{figure}

@@

If the pattern excludes any special values of the data type (e.g., \texttt{cons head tail} excludes empty lists), the generated code should reflect this. Excluded values should never cause the assertion to fail. In the example of \texttt{cons}, the generated code should thus contain the branching shown in \lstref{lst:cons}. The branch in line 1 is executed if the list contains at least one element, and should contain the assertion code. If the list is empty, the branch in line 2 should simply return successfully. 
\begin{lstlisting}[language=Michelson, label=lst:cons, caption=Exclusion of empty lists in the assertion]
IF_CONS ( <assertion body> )
        ( <return ([], ())>)
\end{lstlisting}

@@

\section{Cost analysis and evaluation}\label{sec:cost_analysis_distributed}
In this section, the costs of checking a formula with the proposed approach and implementation for distributed assertion checking are evaluated. \secref{sec:usecase_cost} already determined the cost for a local validation as a benchmark. It stated \eqref{eq:gas_transaction} to calculate the gas consumption of a transaction, including internal operations. It identified the gas consumption of deserialization, data parsing and interpretation as growing factors, which depend on the size of the input parameter.

According to the orchestration scheme, each validator executes $t+2$ operations with the same input parameter $p$. Since deserialization costs are applied lazily, they have to be paid only once for the parameter and the assertion contract code. In addition to the interpretation cost, the reading, parsing and base costs have to be paid for each internal operation. 
\begin{align}\label{eq:gas_validator}
\begin{split}
GasConsumed_{validator}(p) > \quad t * (&base\, gas \\
&+ gasParsing(p) \\
&+ gasRead(C_{assertion}) \\
&+ gasParsing(C_{assertion}) \\
&+ gasInterpretation(C_{assertion})) \\
\end{split}
\end{align}
Based on the resulting inequality in \eqref{eq:gas_validator}, which specifies the costs incurred by each internal operation to the assertion contract as a basis of the total gas consumption per validator, it can be concluded that the overall gas consumption of the distributed validation is higher than in case of a local validation.

The distributed approach was benchmarked by implementing the orchestration scheme for the two minimal dummy contracts \texttt{Foo} and \texttt{Bar} given in \secref{sec:usecase_cost}. Appendix \ref{apx:foobar_distributed} contains the Michelson code for the controller, assertion and parent contracts. In order to preserve comparability between the local and the distributed implementation, the controller contracts were configured with a probability threshold $c = \frac{1}{e}$, s.t. that the necessary number of test runs is equal to the sizes of the search spaces. \figref{fig:cost_distributed} shows the reported gas consumption per validator on the test network Delphinet. Since the effective number of test runs is always a multiple of 32, the cost function approximates a step function.

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{figures/5-offline_tezos/cost_analysis}
\caption{Gas consumption per validator for different input sizes}
\label{fig:cost_distributed}
\end{figure}

The results show, that the cost incurred by a single validator, checking a subset of a search space with size $n$, is already considerably higher than a complete validation in a local approach (cf. \figref{sec:usecase_cost}). In the case of the list parameter (contract \texttt{Bar}), the gas consumption even increases exponentially due to the multiplied reading and parsing costs. Moreover, the probability of accepting an invalid parameter with the given configuration is 37\% in the worst case, which results in a bad cost-performance ratio.

In conclusion to these results, the proposed implementation of the distributed scheme has to be evaluated as inefficient and unable to achieve an improvement regarding the scalability of applications on Tezos. However, distributed assertion checking is nonetheless a promising approach to achieve an improvement, as it has the potential to not only lower the transaction costs for the user, but also to reduce the computational footprint of the transaction within the network. A prerequisite is lowering the gas consumption per validator. This thesis already mentioned some alternative approaches and implementations, which could achieve this; \secref{sec:alt_random} introduces the possibility to coordinate the validators in a systematic iteration of the search space. This chapter described several other orchestration schemes, some of which reduce the number of emitted internal operations. As the inter-contract communication accounts for most of the gas consumption in the modular approach, avoiding them is an effective way of reducing the costs. In this regard, a concrete improvement of the proposed architecture could be to merge the controller and assertion code into a single contract. This corresponds to the inverse hybrid architecture as described in \secref{sec:monolithic}. Instead of $(t+1)$ internal operations, this only requires a single internal operation calling the parent contract.

\section{Open questions}
There remain two aspects of the off-chain design, which could not be addressed in detail by this thesis. These aspects are outlined briefly in the following sections.

\subsection{Representing counterexamples}\label{sec:counterexample}
It remains to be specified, how counterexamples are represented within the network. The interaction scheme in \figref{fig:interaction_modular} suggests, that validators publish a counterexample to the network in case of a failed assertion. For this, the validators have to obtain the randomly generated values from within the execution context of the VM. With the \texttt{failwith} instruction, the top element of the stack can be exposed, allowing to return an interpretable expression from the execution context. The generated values can thus be returned as a single value, a (nested) pair or a list. To allow other validators to check the assertion with a specific set of values, a modified version of the assertion code must be available on the blockchain. Instead of generating random values, this version should take these values as input parameters. Hence, the validator creates a normal transaction invoking this code with the values returned by the \texttt{failwith} instruction and publishes it to the network. The counterexample is then validated like any other transaction on the blockchain.

To implement this scheme, the compiler has to generate one more contract per assertion. In addition, the assertion contract needs to know about the address of the counterexample contract and return the address together with the generated values. This requires a adjustment of the storage type of the assertion contract and changes the order of origination to:
\begin{enumerate}
\itemsep-0.5em
\item \texttt{Origination(parent)}, \texttt{Origination(counterexample)}
\item \texttt{Origination(assertion, address counterexample)}
\item \texttt{Origination(controller, address [assertion], address parent)} 
\end{enumerate}

\subsection{Multi-slot validators}
The proposed implementation for Tezos assumes that all 32 validators of the current block cycle execute a determined number of test runs. In fact, as mentioned in the section describing Tezos' proof-of-stake mechanism, a validator may have been assigned several endorsement slots per cycle. Since these validators only execute the assertion once, the test runs for the other endorsement slots are neglected. As a result, the error rate of the assertion check is unpredictable and may exceed the configured threshold. This issue should be addressed by the protocol design --- multi-slot validators should execute the assertion transaction for each of their endorsement slot.

### 2021-04-26 assertions/doc/thesis-bernhardt/chapters/appendix.tex
Finish revision chpt 5

\section{\texttt{Foo}}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_manager,
				 caption=Manager contract of \texttt{Foo}]{listings/foo_manager.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_assertion,
				 caption=Assertion contract of \texttt{Foo}]{listings/foo_assertion.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_parent,
				 caption=Parent contract of \texttt{Foo}]{listings/foo_parent.tz}

\section{\texttt{Bar}}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_manager,
				 caption=Manager contract of \texttt{Bar}]{listings/bar_manager.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_assertion,
				 caption=Assertion contract of \texttt{Bar}]{listings/bar_assertion.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_parent,
				 caption=Parent contract of \texttt{Bar}]{listings/bar_parent.tz}

>>>>

\section{Foo}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_manager,
				 caption=Controller contract of \texttt{Foo}]{listings/foo_manager.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_assertion,
				 caption=Assertion contract of \texttt{Foo}]{listings/foo_assertion.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:foo_parent,
				 caption=Parent contract of \texttt{Foo}]{listings/foo_parent.tz}

\section{Bar}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_manager,
				 caption=Controller contract of \texttt{Bar}]{listings/bar_manager.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_assertion,
				 caption=Assertion contract of \texttt{Bar}]{listings/bar_assertion.tz}
\lstinputlisting[basicstyle=\linespread{1.0}\fontfamily{lmr}\selectfont\small,
				 backgroundcolor=\color{cverbbg},
				 linewidth=14cm,
				 xleftmargin=0.5cm,
				 frame=lr,
				 framesep=8pt,
				 framerule=0pt,
				 captionpos=b,
				 numbers=none,
				 language=Michelson,
				 label=lst:bar_parent,
				 caption=Parent contract of \texttt{Bar}]{listings/bar_parent.tz}
